---
title: "RiboLausanne Report"
author: "Dermot Harnett"
output: github_document
toc: yes

---



```{r setup, include=FALSE}
#output: rmarkdown::github_document
library(knitr)
library(svglite)
svglite
```

```{r timestamp, echo = TRUE}
Sys.time()
```


## Background

This report will show my analyses of the Riboseq data from the 3 Lausanne cancer cell lines.

The cell lines from the lab of Michal Bassini.

Rnaseq is available on them, as well as exome-seq data.

```we are focusing on three samples (OMM4.75, OD5P and ONVC) which are melanoma samples. ```

```We have identified EREs and LncRNAs derived HLA-I peptides and we will screen them this summer for T cell responses.```

```I have now attached for one cell line, OD5P, the coordinates and ENSG from the genes encoding our hits, a few retroviral elements and quite a few ncRNAs. ```


## results

### Executive Summary

### Todos

- Look at the loci identified, see how many of them have ORFs.

#### Data Quality

Some text below

```{r f1 nap, out.width ='900px', out.height ='900px' ,fig.cap = "", dev='svg',echo=FALSE,include=TRUE,eval=TRUE}
dir.create('plots',showWarnings = FALSE)
#create placeholder
svglite('plots/tmp.svg');plot(1,type='n');text(1,1,"This is a placeholder plot",cex=2);dev.off()
include_graphics("plots/tmp.svg")
include_graphics("plots/tmp.svg")

```

Some text above

This is a link to the full RNAseq report - [save it](report_Lausanne_lab.html)

This is a link to the full SataNN report - [save it](report_Lausanne_lab.html)


### Specific Loci

Plots showing the 3bp Periodicity for OD5P for one cell line


```{r specplots, out.width ='900px', out.height ='900px' ,fig.cap = "", dev='svg',echo=FALSE,include=TRUE,eval=TRUE}
plot(1)
```



## Methods

